From Likes to Change: Assessing the Impact of Citizen Engagement on the European

### 2023-06-17 Article.Rmd
Final article

abstract: |
  This research undertakes an examination of the function that emotional resonance plays in the social media communications disseminated by the European Commission (EC) and its subsequent influence on public involvement across a multitude of platforms such as Facebook, Instagram, Twitter, and YouTube. The findings of this research underscored that communications laden with emotional resonance considerably amplify public engagement, though the magnitude of this amplification is dependent on the individual platform. Furthermore, both positive and negative forms of emotional resonance exhibit a noteworthy influence on public participation. However, it has been observed that the impact of negative emotional resonance is more distinct and profound. Our research underscored the pivotal significance of employing strategies tailored to specific platforms and integrating emotional resonance into public communications as a means to stimulate participation in policy discourse.An analytical examination of both engagement rates and sentiment across various platforms unveils distinctive tonal nuances within the European Commission's discourse.

@@

keywords        : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
wordcount       : "4275 words in text body 1034 words in reference section"
bibliography    : ["r-references.bib", "references.bib"]
floatsintext    : no
linenumbers     : yes
draft           : no
mask            : no
figurelist      : no
tablelist       : no
footnotelist    : no
documentclass   : "apa7"
classoption     : "man"
csl             : apa.csl
header-includes : \usepackage{ragged2e}
output          :
  pdf_document  : papaja::apa6_pdf
  html_document :
    df_print    : paged
  word_document : papaja::apa6_docx
---

>>>>

abstract: |
  This research undertakes an examination of the function that emotional resonance plays in the social media communications disseminated by the European Commission (EC) and its subsequent influence on public involvement across a multitude of platforms such as Facebook, Instagram, Twitter, and YouTube. The findings of this research underscored that communications laden with emotional resonance considerably amplify public engagement, though the magnitude of this amplification is dependent on the individual platform. Furthermore, both positive and negative forms of emotional resonance exhibit a noteworthy influence on public participation. However, it has been observed that the impact of negative emotional resonance is more distinct and profound. Our research underscored the pivotal significance of employing strategies tailored to specific platforms and integrating emotional resonance into public communications as a means to stimulate participation in policy discourse.An analytical examination of both engagement rates and sentiment across various platforms unveils distinctive tonal nuances within the European Commission's discourse.

@@

keywords        : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
wordcount       : "4275 words in text body 1034 words in reference section"
bibliography    : ["r-references.bib", "references.bib"]
floatsintext    : no
linenumbers     : yes
draft           : no
mask            : no
figurelist      : no
tablelist       : no
footnotelist    : no
documentclass   : "apa7"
classoption     : "man"
csl             : apa.csl
header-includes : \usepackage{ragged2e}
output          :
  word_document : papaja::apa6_docx
  html_document :
    df_print    : paged
  pdf_document  : papaja::apa6_pdf
---
